\chapter*{Abstract}
The main problem of retrieval-augmented generation (RAG) in large language models is its inability to work properly due to the presence of complicated sentence structures in queries. In this case, the retrieval part makes wrong identifications, which results in mistakes during the following generation. Therefore, the current project provides a solution to this issue using the proposed quantum-retrieval augmented generation framework called QRAG.

\bigskip\noindent
The key idea relies on using the quantum variational classifier for dealing with the challenges posed by ambiguous queries. Sentences can be encoded to quantum circuits to take account of those relations and dependencies in language that traditional vector representation might miss, especially in the case of nonlinearity. The ambiguity controller decides which pathway – classical or quantum – will be followed, depending on how complicated the query is.

\bigskip\noindent
According to the experiment conducted on the proposed solution, the accuracy improved significantly, reaching 46\% in complicated datasets where the syntactic ambiguities were harder to resolve. This finding demonstrates the threshold for complexity below which the contribution of quantum approaches to the solution would be significant while classical approaches would suffice otherwise. Despite some negative opinion regarding the use of quantum technologies, these metrics prove the efficiency of this approach.

\bigskip\noindent
The architecture created in this paper represents a scalable hybrid model, where the quantum and classical parts work together. It improves RAG's ability to retain semantic information during the process. Nonetheless, there are several unexplored components, which could be addressed in the future.