\chapter*{Conclusion}

A new two-stage hybrid architecture known as RAG, which aims to improve semantic search and syntactic ambiguity resolution, is described in this paper. This study highlights the limitation of existing classical AI models by showing that, despite efficiency, these models suffer from utility limitations, thereby requiring a quantum solution.

The architecture relies on the use of a classical RAG model using a pipeline system that uses both MongoDB Vector retrieval and a dynamic Neo4j Knowledge Graph. One of the most remarkable innovations in this stage is the Constructive Hallucination technique, which uses the failure characteristics of Large Language Models to automate knowledge graph enrichment. The classical engine is an efficient semantic search engine that works well for linear queries.

However, empirical testing has revealed a limitation of purely classical models. This is referred to as the Linearity Trap. Classical models tend to produce fluent yet semantically incorrect answers to syntactically ambiguous sentences such as preposition attachment and reduced relative clauses. This problem arises because of the linear nature of n-gram similarity and attachment preferences.

In order to overcome the restrictions inherent in the existing approaches, the architecture utilizes an Ambiguity Controller to redirect more structurally complex queries to the dedicated Quantum Retrieval-Augmented Generation (QRAG) module. Using PQC representations for dependency trees along with entanglement, the Quantum NLP co-processor allows for accurate evaluation of overall sentence structure. Experimental results clearly confirm the existence of the “Viola Moment” with a considerable improvement in disambiguation performance quantitatively measured against purely classical heuristics.

Importantly, this research formalizes the notion of the Utility Threshold. Quantum computing is not proposed to be seen as a substitute for classical operations; on the contrary, it works as a very specific kind of co-processor where its advantages become evident only beyond certain threshold levels of syntactical complexity. For simpler semantic search tasks, classical systems remain preferable; however, for complex ambiguity problems, quantum entanglement must be used.

For experimental confirmation of these theoretical results within the context of real-life application, the whole dual-entity system was applied to develop an interactive web platform communicating with an extensive knowledge base comprising some 130,000 documents. Real-life deployment gave important insights through specially designed evaluation dashboards which helped observe the “Linearity Trap,” compare the outcomes of the baseline classical computations against graph enrichment methods, and determine the exact point beyond which complex queries are forwarded to the quantum co-processor.

To conclude, the live implementation confirms the viability of the proposed system as it successfully implements both classical heuristics for high-speed search and augmented knowledge graphs for interpretation enrichment along with the utilization of the quantum framework for more complex queries. Overall, such an approach provides a basis for further evolution of natural language processing algorithms.